Adding Interactivity to Static Rmarkdown Documents

### 2017-09-17 02_rmarkdown-interactivity/post.Rmd
Progress on rmarkdown interactivity

@@

@@

  highchart() %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    categories = plot_data$value,
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities") %>%
  hc_add_series(
    name = "Normal", 
    type = "spline",
    data = plot_data$normal,
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Exponential",
    type = "spline",
    data = plot_data$exponential,
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Uniform",
    type = "spline",
    data = plot_data$uniform,
    marker = list(enabled = FALSE)
  )

@@

@@

  $("#update_age_series").click(function(){

    var chart=$("#age_series_chart").find(".highchart").highcharts();

@@

      chart.yAxis[0].setExtremes(0,null);
      chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
      #dir_pdf = `r dir_pdf`;
      #female_pdf = `r female_pdf`;
      #male_pdf = `r male_pdf`;
      chart.series[0].setData(dir_pdf);
      chart.series[1].setData(male_pdf);
      chart.series[2].setData(female_pdf);
      $("#update_age_series").html("Show Cumulative Distribution");

@@

      chart.yAxis[0].setExtremes(0,1);
      chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
      #dir_cdf = `r dir_cdf`;
      #female_cdf = `r female_cdf`;
      #male_cdf = `r male_cdf`;
      chart.series[0].setData(dir_cdf);
      chart.series[1].setData(male_cdf);
      chart.series[2].setData(female_cdf);

>>>>

# Overview

Interactivity in data analytics outputs is great for a number of reasons.

As an R User you have a number of different formats to write. It can become confusing about how each of these formats differ from one another, specifically when it comes to interactivity.

- **Shiny Apps** is the most interactive format with few limitations but requires a server to run.
- **HTML R markdown docs, slides and Notebooks** are nice comprimise.
- **Non-HTML Rmarkdown outputs** are the least interactive with text and plots (images) assembled in a static arrangement.

This post specifically focuses on option 2 and how it can be enhanced to be more like '

@@

density %>% head()

@@

  highchart() %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities") %>%
  hc_add_series(
    name = "Normal", 
    type = "spline",
    data = plot_data %>% select(x = value, y = normal) %>% list_parse()
    #marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Exponential",
    type = "spline",
    data = plot_data %>% select(x = value, y = exponential) %>% list_parse()
   # marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Uniform",
    type = "spline",
    data = plot_data %>% select(x = value, y = uniform) %>% list_parse()
   # marker = list(enabled = FALSE)
  ) -> chart

chart

@@

# Get CDF from density dataframe
get_dist = function(df, var, type) {

  if (type=="pdf") {

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    mutate(
      js_pair = paste0("[", value, "," , density %>% round(6), "]")
    ) %>%
    pull(js_pair) %>% # Just found this function, handy!
    return()

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    arrange(value) %>%
    mutate(
      cdf = cumsum(density),
      js_pair = paste0("[", value, "," , cdf %>% round(4), "]")
    ) %>%
    pull(js_pair) %>% # Just found this function, handy!
    return()

  }

}

# Conver R char vector of x, y pairs to JS array string
js_stringify = function(vec) {

  vec %>%
    paste(collapse = ",") %>%
    paste0("[", . , "]") %>%
    JS() %>%
    return()

}

# Javascriptise PDF Data
nor_pdf = get_dist(density, "normal", "pdf") %>% js_stringify()
exp_pdf = get_dist(density, "exponential", "pdf") %>% js_stringify()
uni_pdf = get_dist(density, "uniform", "pdf") %>% js_stringify()

# Javascriptise CDF Data
nor_cdf = get_dist(density, "normal", "cdf") %>% js_stringify()
exp_cdf = get_dist(density, "exponential", "cdf") %>% js_stringify()
uni_cdf = get_dist(density, "uniform", "cdf") %>% js_stringify()

# In action

  highchart(elementId = "densities_v2") %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    #categories = plot_data$value,
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities") %>%
  hc_add_series(
    name = "Normal", 
    type = "spline",
    #data = plot_data$normal,
    data = plot_data %>% select(x = value, y = normal) %>% list_parse(),
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Exponential",
    type = "spline",
    #data = plot_data$exponential,
    data= plot_data %>% select(x = value, y = exponential) %>% list_parse(),
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Uniform",
    type = "spline",
    #data = plot_data$uniform,
    data = plot_data %>% select(x = value, y = uniform) %>% list_parse(),
    marker = list(enabled = FALSE)
  )

<button id="test"> Click Me </button>

<script>

    var show_cdf = true;

    $("#test").click(function(){

      var chart=$("#densities_v2").highcharts();

      if (!show_cdf) {

        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
        uni_cdf = `r uni_cdf`;
        nor_cdf = `r nor_cdf`;
        exp_cdf = `r exp_cdf`;
        chart.series[0].setData(nor_cdf);
        chart.series[1].setData(exp_cdf);
        chart.series[2].setData(uni_cdf);
        $("#test").html("Show Density");

        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
        uni_pdf = `r uni_pdf`;
        nor_pdf = `r nor_pdf`;
        exp_pdf = `r exp_pdf`;
        chart.series[0].setData(nor_pdf);
        chart.series[1].setData(exp_pdf);
        chart.series[2].setData(uni_pdf);
        $("#test").html("Show CDF");

    show_cdf = !show_cdf;

</script>

@@

  $("#test").click(function(){

    var chart=$("#densities_v2").find(".highchart").highcharts();

@@

      chart.yAxis[0].setExtremes(0,null);
      chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
      uni_cdf = `r uni_cdf`;
      nor_cdf = `r nor_cdf`;
      exp_cdf = `r exp_cdf`;
      chart.series[0].setData(uni_cdf);
      chart.series[1].setData(nor_cdf);
      chart.series[2].setData(exp_cdf);

@@

      chart.yAxis[0].setExtremes(0,1);
      chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
